The Weakly Nonlinear Magnetorotational Instability in a local geometry

### 2017-03-15 paper/thingap_ref_response/thingap_mri_paper_ref_response_apj.tex
some sim text while we wait

Our final equation set is

%\begin{widetext}
\onecolumngrid
\beq
\label{eqset1}
\partial_t \nabla^2 \Psi \, - \, 2 \partial_z u_{y} \, - \, \Co B_0 \partial_z \nabla^2 A \, - \, \frac{1}{\reye}\nabla^4 \Psi \, = \, \Co J\left(A, \nabla^2 A \right) \, - \, J\left(\Psi, \nabla^2 \Psi\right) \, 
\eeq
%\end{eqnarray}
%\end{widetext}

@@

\edit1{We perform nonlinear, axisymmetric simulations of our fiducial setup using Dedalus.}

>>>>

\onecolumngrid
Our final equation set is

%\begin{widetext}

\beq
\label{eqset1}
\partial_t \nabla^2 \Psi \, - \, 2 \partial_z u_{y} \, - \, \Co B_0 \partial_z \nabla^2 A \, - \, \frac{1}{\reye}\nabla^4 \Psi \, = \, \Co J\left(A, \nabla^2 A \right) \, - \, J\left(\Psi, \nabla^2 \Psi\right) \, 
\eeq
%\end{eqnarray}
%\end{widetext}

@@

\edit1{We perform two-dimensional, axisymmetric simulations of our fiducial setup using Dedalus. We solve the nonlinear Equations \ref{eqset1} - \ref{eqset4} with the background magnetic field set to $B_0 = 1 + \epsilon^2$ so that the system is MRI unstable. We initialize the runs with the linear eigenvalue solutions of the MRI equations multiplied by a small initial amplitude $A_0 = 1\times 10^{-3}$. We initialize the linear eigenvalue form for computational efficiency, as the simulation quickly enters its linear growth phase. We confirm that these simulations behave the same as simulations with noise initial conditions once they enter linear growth. We use a four-stage, third-order Runge-Kutta integration scheme to timestep the system until saturation.}
